---
title: "Week 1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor) # janitor helps us clean datasets
library(here) # here helps us to know where files are

```

## Getting Data

```{r COVID-19}
COVID19data <- readr::read_csv(file ="https://data.ontario.ca/dataset/f4112442-bdc8-45d2-be3c-12efae72fb27/resource/455fd63b-603d-4608-8216-7d8647f43350/download/conposcovidloc.csv")
```

## Writing the data

```{r}
write_csv(COVID19data, here("dataset/COVID19data.csv"))
```

## head operation

```{r}
head(COVID19data)
```

## selecting few columns
```{r}
COVID19data %>% select(Case_Reported_Date,Age_Group,Age_Group,Case_AcquisitionInfo,Reporting_PHU_City)
```
#now cleaning up the age column by removing "s"
```{r}
COVID19data$Age_Group = gsub("s","",COVID19data$Age_Group)
COVID19data$Age_Group = as.numeric(COVID19data$Age_Group)
```

## filtering rows (| will return when atleast one condition is met)
```{r}
COVID19data %>% filter(Age_Group >= 30 | Client_Gender == "FEMALE")
```
## filtering rows (| will return when both conditions met)
```{r}
COVID19data %>% filter(Age_Group >= 30 & Client_Gender == "FEMALE")
```
## group by function
```{r}
COVID19data %>% group_by(Age_Group,Client_Gender) %>% count(Age_Group)
```

## cleaning the names of the columns
```{r}
COVID19data = janitor::clean_names(COVID19data)
```

# graph
```{r}
COVID19data %>% ggplot(mapping = aes(x = Age_Group,fill = Client_Gender)) + geom_bar()
```
## Graph - label & heading - Facets are subplots and they allow you to add another variable to your plot without having to make a 3D plot.
```{r}

COVID19data %>% group_by(Age_Group,Client_Gender) %>% ggplot(mapping = aes(x = Age_Group,fill = Client_Gender)) + geom_bar() + labs(title = "Total COVID-19 Positive cases in Ontario",x = "Age", Count = "Count") + theme_dark() + scale_fill_brewer(palette = "Set2") + facet_wrap(~Client_Gender)
```

## Left join
```{r}
Superstore_Sales <- read_excel("D:/George Brown College/2020/Health Informatics - COMP 4033 (May 2020)/data sets/Superstore Sales.xls")
Superstore_Sales1 <- read_excel("D:/George Brown College/2020/Health Informatics - COMP 4033 (May 2020)/data sets/Superstore Sales.xls")
newsuperstore = Superstore_Sales1 %>% left_join(Superstore_Sales,by = "Order ID")
```

## making a tibble - A tibble is a data frame, but it is a data frame with some particular changes that make it easier to work with.
```{r}
COVID19ontario = tibble(names = c("patient a","patient b","patient c"),covidpos = c("yes","no","yes"),datereported = c("02/02/2020","02/03/2020","04/08/2020"))
```


## Spotify code
```{r}
library(spotifyr)
usethis::edit_r_environ()
```

```{r}

radiohead <- get_artist_audio_features('radiohead')
```

